Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-29 paper.tex
Update paper.tex

\begin{figure}[h]
	\centering
	\includegraphics[width=15cm]{temperature_plot.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature. Approximate domestication center for each crop is denoted by a triangle}
	\label{fig:map}
\end{figure}

@@

Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) was domesticated at least twice roughly 8,000 to 10,000 BP: once from the wild subsp. \emph{spontaneum} in the Fertile Crescent and once from subsp. \emph{spontaneum} var. \emph{agriocrithon} in Tibet \cite{badr2000origin, Morrell2007, dai2012tibet}.
Presently, the distribution of subsp. \emph{spontaneum} stretches from the eastern Mediterranean through the Middle-East to west-central Asia, spanning clines in temperature, precipitation, soil type, and altitude \cite{Morrell2007}.
Cultivated barley is found throughout much of the \emph{spontaneum} distribution and barley-\emph{spontaneum} hybrids are fertile and commonly found when these taxa co-occur.

Poets and co-authors \cite{Poets2015} recently investigated the range-wide contribution of wild barley to landraces, assessing both genome-wide and geographical patterns of introgression.
This study identified several lines of evidence consistent with wild introgression aiding the expansion and adaptation of domesticated barley.
Using ancestry deconvolution methods, the authors identified genomic regions of shared ancestry linking particular landraces to numerous wild relative populations.
These results suggested landraces may have received wild introgression on a continual basis during post-domestication expansion.
However, barley landraces also showed an excess of ancestry from nearby wild relatives, indicating a prevalence of local and potentially adaptive gene flow.
Limited admixture linkage disequilibrium and small tracts of identity by state suggest substantial recombination has occurred since initial crop-wild hybridization and that even locally introgressed chromosomal regions are ancient, perhaps dating to the early expansion of barley post-domestication.
While these results are consistent with adaptive introgression, wild barley haplotypes have yet to be definitively linked to specific adaptations in domesticated landraces.

\item{Asian Rice:}

The details of Asian rice (\emph{Oryza sativa}) domestication are still debated.
Certain genetic and archaeobotanical evidence point toward independent domestications of the two prominent varietal groups \emph{japonica} and \emph{indica} from the wild species \emph{Oryza rufipogon} (\emph{rufipogon} hereafter) in China and the Indian Ganges plain, respectively \cite{fuller2010consilience}, with a potential third domestication event giving rise to the varietal group \emph{aus} in Bangladesh or central India \cite{civavn2015three}.
Other studies support a single domestication in China, with later divergence of \emph{japonica} and \emph{indica} \cite{molina2011molecular, Huang2012} during crop expansion.
For example, Huang and colleagues \cite{Huang2012} developed a genetic map of rice variation, which they used to measure genetic distance between a range-wide sample of wild and domesticated rice, finding that \emph{japonica} was domesticated near the Pearl River in Guangxi province, China, and that \emph{indica} was likely the result of hybridization between \emph{japonica} and local \emph{rufipogon} populations in Southern and South-eastern Asia.
In a re-examination of these same data, \cite{civavn2015three} found evidence supporting independent domestications of \emph{japonica}, \emph{indica}, and \emph{aus}, as well as a hybrid origin (\emph{japonica} x \emph{aus}) of \emph{aromatic} rice.
A recent third analysis by Choi and co-authors \cite{choi2018multiple} compared these two disparate results and the methods utilized therein, concluding that domestication alleles (including \emph{LABA1}, \emph{PROG1}, and \emph{sh1}) arose during a single domestication event of \emph{japonica}, and that these alleles introgressed into several wild \emph{rufipogon} subpopulations which thereby became the progenitors of other Asian rice varieties.

The findings of \cite{choi2018multiple} bear similarities to a hypothesis posited by Vaughan and colleagues \cite{vaughan2008evolving}.
According to this hypothesis, domestication alleles arose in a single cultivated rice population and subsequently introgressed into diverse cultivated populations (some \emph{japonica}-like, some \emph{indica}-like).
As these now fully domesticated populations spread further into new environments, they potentially received introgression from locally adapted wild relatives, retaining alleles that improved fitness.
While the precise history of domesticated rice remains in question, multiple lines of evidence indicate diverse wild populations have contributed to domesticated germplasm and suggest adaptive introgression may have played a role during the expansion of this important crop.

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=15cm]{temperature_plot_degC.pdf}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature. Approximate domestication center for each crop is denoted by a triangle}
	\label{fig:map}
\end{figure}

@@

Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) was domesticated from wild subsp. \emph{spontaneum} roughly 8,000 to 10,000 BP.
Modern barley is most likely the result of multiple domestication events across the Middle East and Asia \cite{azhaguvel2007phylogenetic}.
There is clear evidence of one domestication event of barley from the wild subsp. \emph{spontaneum} in the Fertile Crescent \cite{badr2000origin, Morrell2007}, and many have supported an additional eastern center of barley domestication from subsp. \emph{spontaneum} var. \emph{agriocrithon} \cite{Morrell2007}, possibly Tibet \cite{dai2012tibet}.
However, recent research from Pourkheirandish and colleagues \cite{pourkheirandish2018elucidation} suggests that the putative wild Tibetan progenitor \emph{agriocrithon} is a misidentified intercultivar hybrid of domesticated 6-row landraces, which they deem \emph{pseudo-agriocrithon}, as opposed to \emph{eu-agriocrithon}, which are six-rowed wild relatives derived from two-rowed \emph{ssp. spontaneum}.
The non-brittle rachis mutations (\emph{btr1} and \emph{btr2}) appear to have arisen in populations from the Levant, whereas the two most common of four alleles conferring 6-rowed spike morphology (\emph{vrs1.a1} and \emph{vrs1.a4}) originated in \emph{eu-agriocrithon} populations in Central Asia (Turkmenistan and Uzbekistan, respectively).
These two key barley domestication traits were combined when \emph{vrs1.a1} and \emph{vrs1.a4} introgressed from \emph{eu-agriocrithon} into cultivated barleys in the Levant.

Presently, the distribution of subsp. \emph{spontaneum} stretches from the eastern Mediterranean through the Middle-East to west-central Asia, spanning clines in temperature, precipitation, soil type, and altitude \cite{Morrell2007}.
Cultivated barley is found throughout much of the \emph{spontaneum} distribution and barley-\emph{spontaneum} hybrids are fertile and commonly found when these taxa co-occur.

Poets and co-authors \cite{Poets2015} recently investigated the range-wide contribution of wild barley to landraces, assessing both genome-wide and geographical patterns of introgression.
This study identified several lines of evidence consistent with wild introgression aiding the expansion and adaptation of domesticated barley.
Using ancestry deconvolution methods, the authors identified genomic regions of shared ancestry linking particular landraces to numerous wild relative populations.
These results suggested landraces may have received wild introgression on a continual basis during post-domestication expansion.
However, barley landraces also showed an excess of ancestry from nearby wild relatives, indicating a prevalence of local and potentially adaptive gene flow.
Limited admixture linkage disequilibrium and small tracts of identity by state suggest substantial recombination has occurred since initial crop-wild hybridization and that even locally introgressed chromosomal regions are ancient, perhaps dating to the early expansion of barley post-domestication.
While these results are consistent with adaptive introgression, wild barley haplotypes have yet to be definitively linked to specific adaptations in landraces post-domestication.

%"The best current hypothesis holds that both vrs1.a1 and vrs1.a4 were introgressed from eu-agriocrithon into other wild barley genotypes and then outcrossed to cultivated barley (Figure 1)"

%"The proposal here is that vrs1.a1 and vrs1.a4 emerged in agriocrithon before they were introgressed into ssp. vulgare (Figure 1)."

%"The origin of two alleles (vrs1.a2 and a3) was previously shown (Komatsuda et al., 2007) to involve single mutations at the vrs1 locus that changed the domesticated two-rowed to six-rowed phenotype (Figure 1)."

%"Both vrs1.a1 and vrs1.a4 arose in Central Asia, some 2500 km distant from the site of emergence of non-brittle rachis. The occurrence of six-rowed types among wild barley implies that the six-rowed allele pre-dates domestication, when early farmers still relied on ssp. spontaneum. This time line agrees, in part at least, with the notion that six-rowed cultivated barley was derived from agriocrithon (Aberg, 1938). The non-brittle rachis trait represents a strong genetic bottleneck, and its geographical origin lies far from that of eu-agriocrithon, clearly implying that eu-agriocrithon could not have been the immediate ancestor of the non-brittle barleys that were donors of vrs1.a1 and vrs1.a4 to cultivated barley."
